babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-08 article.tex
EOD

This code will create a (temporary) BEAST2 configuration file,
using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
\verb;babette; will then execute a BEAST2 with that file, and
parses the output. The default settings are, among others, 
to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
a strict clock, and a Yule birth tree prior \cite{yule}.

@@

\verb;babette; uses the Travis CI \cite{travis} 
continuous integration service, which is known to significantly 
increase the the number of bugs exposed \cite{vasilescu2015} and increases
the speed at which new features are added \cite{vasilescu2015}.
\verb;babette; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
\verb;babette; follows Hadley Wickham's style guide \cite{style_guide}, which improves software quality \cite{fang2001}.
\verb;babette; is dependent on multiple packages, which are 
\verb;APE; \cite{APE}, 
\verb;beautier; \cite{beautier},
\verb;beastier; \cite{beastier},
\verb;devtools; \cite{devtools},
\verb;geiger; \cite{GEIGER},
\verb;ggplot2; \cite{ggplot2},
\verb;knitr; \cite{knitr},
\verb;phangorn; \cite{phangorn},
\verb;rmarkdown; \cite{rmarkdown},
\verb;seqinr; \cite{seqinr},
\verb;stringr; \cite{stringr},
\verb;testit; \cite{testit} and 
\verb;tracerer; \cite{tracerer},
\verb;TreeSim; \cite{TreeSim}.

>>>>

This code will create a (temporary) BEAST2 configuration file,
using a FASTA file with name \verb;alignment.fas;, 
using the same default settings as BEAUti.
\verb;babette; will then execute a BEAST2 with that file, and
parses the output. The output, named \verb;out;, is a list of
parameter estimates, posterior phylogenies (one per alignment)
and operator acceptances.

The default settings for BEAUti (and thus \verb;babette;) are, 
among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
a strict clock, and a Yule birth tree prior \cite{yule}.

@@

\verb;babette; uses the Travis CI \cite{travis} 
continuous integration service, which is known to significantly 
increase the the number of bugs exposed \cite{vasilescu2015} and increases
the speed at which new features are added \cite{vasilescu2015}.
\verb;babette; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
\verb;babette; follows Hadley Wickham's style guide \cite{style_guide}, which improves software quality \cite{fang2001}.
\verb;babette; is dependent on multiple packages, which are 
\verb;APE; \cite{APE}, 
\verb;beautier; \cite{beautier},
\verb;beastier; \cite{beastier},
\verb;devtools; \cite{devtools},
\verb;geiger; \cite{GEIGER},
\verb;ggplot2; \cite{ggplot2},
\verb;knitr; \cite{knitr},
\verb;phangorn; \cite{phangorn},
\verb;rmarkdown; \cite{rmarkdown},
\verb;seqinr; \cite{seqinr},
\verb;stringr; \cite{stringr},
\verb;testit; \cite{testit} and 
\verb;tracerer; \cite{tracerer} and
\verb;TreeSim; \cite{TreeSim}.
